Perturbing SU($n$)-symmetric interactions

### 2020-01-24 collective_sun/sun_perturbation.tex
better formalize the use of integers modulo L

We consider an array of $N$ multilevel spins with non-uniform
SU($n$)-symmetric interactions that can be written in the form
\begin{align}
  H_0 = \sum_{p<q} h_{pq} \Pi_{pq},
  &&
  \Pi_{pq} \equiv \sum_{\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)},
  \label{eq:ints}
\end{align}
where $p,q$ index individual spins; $\mu,\nu$ index states in an
orthonormal basis for the $n$-dimensional Hilbert space $\H_n$ of a
single spin; $h_{pq}$ are scalar coefficients; the operator
$S_{\mu\nu}^{(p)}\equiv\op{\mu}{\nu}_p$ flips the state of spin $p$ to
$\ket\mu$ from $\ket\nu$; and the operator $\Pi_{pq}$ permutes the
states of spins $p$ and $q$.  The permutation operator $\Pi_{pq}$ is a
multilevel generalization of the SU(2)-symmetric spin interaction
$\v S_p\c\v S_q$ for $\v S=\p{S_\x,S_\y,S_\z}$.

@@

Here we show that power-law SU($n$)-symmetric interactions of the form
in \eqref{eq:ints} with $h_{pq}=-h/\abs{p-q}^\alpha$ yield a
non-vanishing many-body interaction energy gap when $\alpha\le D$,
where $D$ is the dimension of the lattice.  On a periodic lattice of
$N=L^D$ spins, the spectral gap of the interaction Hamiltonian is (see
Appendix \ref{sec:trans_inv_single})
\begin{align}
  \Delta
  = \sum_{d\in\tilde\ZZ_L^D} h_{0,d} \sp{\cos\p{d \c k_{\t{SE}}}-1}
  = h \sum_{\substack{d\in\tilde\ZZ_L^D\\d\ne0}}
  \f{1-\cos\p{d \c k_{\t{SE}}}}{\abs{d}^\alpha},
\end{align}
where the domain of $d$ is given by
$\tilde\ZZ_L\equiv\set{-\floor{L/2},-\floor{L/2}+1,\cdots,\ceil{L/2}}$,
and $k_{\t{SE}}$ is a wavenumber for a singly-excited spin-wave state.
In order to yield the smallest excitation energy $\Delta$, the
wavenumber $k_{\t{SE}}$ should maximize the contribution of the cosine
term above, which is achieved by a wavenumber that minimizes the
oscillations of this term when integrated over the entire lattice.  A
suitable candidate for a minimal wavenumber is
$k_{\t{SE}}=\p{2\pi/L,0,0,\cdots}$, which corresponds to an excitation
energy
\begin{align}
  \Delta = h \sum_{\substack{d\in\tilde\ZZ_L^D\\d\ne0}}
  \f{1-\cos\p{d_12\pi/L}}{\abs{d}^\alpha}.
\end{align}
Defining $\epsilon\equiv2/L$ and a rescaled domain
$\SS_\epsilon\equiv\tilde\ZZ_L/\epsilon\subset\sp{-1,1}$, we
substitute $x\equiv\epsilon d\in\SS_\epsilon^D$ to get
\begin{align}
  \Delta
  = h \sum_{\substack{x\in\SS_\epsilon^D\\x\ne0}}
  \f{1-\cos\p{\pi x_1}}{\abs{x/\epsilon}^\alpha}
  = h \epsilon^{D-\alpha} \sum_{\substack{x\in\SS_L^D\\x\ne0}}
  \epsilon^D \f{1-\cos\p{\pi x_1}}{\abs{x}^\alpha}.
\end{align}
As $\epsilon\to0$ the discrete sum over $x$ becomes an integral that
avoids an infinitesimal region about the origin, i.e.
\begin{align}
  \Delta = h \epsilon^{\alpha-D} \I_{D\epsilon},
  &&
  \I_{D\epsilon}
  \equiv \int_{\TT_1^D\setminus\TT_\epsilon^D} \d^Dx\,
  \f{1-\cos\p{\pi x_1}}{\abs{x}^\alpha},
\end{align}
where the integral $\I_{D\epsilon}$ is defined using the interval
$\TT_a\equiv\p{-a,a}$.  The integrand of $\I_{D\epsilon}$ is strictly
positive and well-behaved on the entirety of its domain except for the
origin, where depending on the value of $\alpha$ the integrand may
vanish or diverge as $\abs{x}\to0$.  Together, these facts mean that
\begin{align}
  \I_{D\epsilon} \stackrel{\epsilon\to0}{\sim} \epsilon^{-\gamma},
  &&
  \Delta \stackrel{\epsilon\to0}{\sim} h \epsilon^{\alpha-D-\gamma},
\end{align}
for some $\gamma\ge0$, which implies that gap $\Delta$ is
non-vanishing when $\alpha\le D\le D+\gamma$.

@@

For reference, the single-body eigenvalue problem is
\begin{align}
  \p{\m h - \diag\v h}\c\v v = \Delta \v v,
  \label{eq:cond_1_ref}
\end{align}
where $\m h$ is a matrix of all couplings $h_{pq}$ that appear in the
interaction Hamiltonian $H_0$ in \eqref{eq:ints}; $\v h$ is a vector
of all $h_p\equiv\sum_q h_{pq}$; $\diag\v h$ is a matrix with $\v h$
on the diagonal and zeroes everywhere else; and $\v v$ is a vector of
coefficients used to construct the single-body perturbation
$\V_1\p{\v v}$ defined in \eqref{eq:perturbations}.  When the
interaction Hamiltonian $H_0$ is translationally invariant, the
couplings $h_{pq}$ depend only on the separation $\pm\p{p-q}$, so the
eigenvectors of $\m h$ are plane waves of the form
\begin{align}
  \v v_k \equiv \sum_p e^{ip\c k} \ket{p},
\end{align}
where on a $D$-dimensional periodic lattice of $N=L^D$ spins, lattice
sites are indexed by vectors
$p\in\tilde\ZZ_L^D \equiv
\set{-\floor{L/2},-\floor{L/2}+1,\cdots,\ceil{L/2}}$, and wavenumbers
take on values $k\in\tilde\ZZ_L^D\times2\pi/L$.  The corresponding
eigenvalues of $\m h$ can be determined by expanding
\begin{align}
  \m h\c\v v_k = \sum_{p,q} h_{pq} e^{iq\c k} \ket{p}
  = \sum_{p,d} h_{p,p+d} e^{i\p{p+d}\c k} \ket{p}
  = \sum_d h_{0,d} e^{id\c k} \v v_k
  = \sum_d h_{0,d} \cos\p{d\c k} \v v_k,
\end{align}
where the imaginary terms vanish because $h_{0,d}=h_{0,-d}$.  The
remainder of \eqref{eq:cond_1_ref} that we need to sort out is
$\diag\v h$, where all $h_p=\sum_qh_{pq}=\sum_dh_{0,d}$ are equal,
which implies that $\diag\v h=\sum_dh_{0,d}$ is a scalar.  We thus
find that
\begin{align}
  \p{\m h - \diag\v h}\c\v v_k = \Delta_k \v v_k,
  &&
  \Delta_k \equiv \sum_d h_{0,d} \sp{\cos\p{d\c k}-1}.
\end{align}

@@

The two-body eigenvalue equation in \eqref{eq:cond_2} is designed to
find solutions $\m w$ to the equation
\begin{align}
  \p{2h_{pq}-h_p-h_q} w_{pq}
  + \sum_k \p{h_{pk} w_{kq} + w_{pk} h_{kq}}
  = \Delta w_{pq},
  \label{eq:cond_2_ref_start}
\end{align}
where $h_p\equiv\sum_q h_{pq}$.  If the interaction Hamiltonian $H_0$
is translationally invariant, then the couplings $h_{pq}$ depend on
$p$ and $q$ only through the separation $\pm\p{p-q}$.  In this case,
all $h_p=h_0$ are equal, and \eqref{eq:cond_2_ref_start} can be
written in the form
\begin{align}
  2 \m h\circ \m w + \P_{\t{off-diag}}\p{\m h\c\m w + \m w\c\m h}
  = \p{\Delta + 2h_0} \m w,
  \label{eq:cond_2_ref}
\end{align}
where $\m h$ and $\m w$ are matrices of all $h_{pq}$ and $w_{pq}$, and
$\m h\circ\m w$ denotes an element-wise (Kronecker) product of $\m h$
and $\m w$, and
$\P_{\t{off-diag}}\p{\m m}\equiv \m m-\sum_p\op{p}\m m\op{p}$ denotes
the projection of $\m m$ onto the space of strictly off-diagonal
matrices.  In order to find solutions to \eqref{eq:cond_2_ref}, we we
expand the matrices $\m h,\m w$ in a basis that the respects
translational symmetry of $\m h$.  To this end, for all lattice
displacements $d\in\tilde\ZZ_L^D$ and wavenumbers
$k\in\tilde\ZZ_L^D\times2\pi/L$ we define the {\it cycle matrices}
\begin{align}
  \m m_{dk} \equiv \sum_p e^{ip\c k} \op{p+d}{p},
  \label{eq:cycle}
\end{align}
where the element-wise sums in $p+d$ are implicitly taken modulo $L$
(i.e.~the length of the periodic lattice along each axis).  In terms of the cycle matrices, we define
\begin{align}
  \tilde w_{dk} \equiv \f1N \tr\p{\m m_{dk}^\dag \m w},
\end{align}
expand
\begin{align}
  \m h = \sum_{p,q} h_{pq} \op{p}{q}
  = \sum_{q,d} h_{q+d,q} \op{q+d}{q}
  = \sum_d h_{d,0} \m m_{d,0},
  &&
  \m w = \sum_{d,k} \tilde w_{dk} \m m_{dk},
\end{align}
and write the condition in \eqref{eq:cond_2_ref} as a new set of
conditions
\begin{align}
  \sum_{d\ne0} 2 h_{d,0} \tilde w_{dk} \m m_{dk}
  + \sum_{\substack{c,d\\c+d\ne0}}
  h_{c,0} \tilde w_{dk} \p{1 + e^{-ic\c k}} \m m_{c+d,k}
  = \p{\Delta + 2 h_0} \sum_{d\ne0} \tilde w_{dk} \m m_{dk},
\end{align}
that must hold for all wavenumbers $k$.  With some re-indexing, we can
write
\begin{align}
  \sum_{d\ne0} 2 h_{d,0} \tilde w_{dk} \m m_{dk}
  + \sum_{c,d\ne0} h_{d-c,0} \tilde w_{ck}
  \p{1 + e^{-i\p{d-c}\c k}} \m m_{dk}
  = \p{\Delta + 2 h_0} \sum_{d\ne0} \tilde w_{dk} \m m_{dk},
  \label{eq:cond_2_cycle}
\end{align}
and define
\begin{align}
  \ut{\check{\m h}}_k
  \equiv \sum_{d\ne0} 2 h_{d,0} \op{d}
  + \sum_{c,d\ne0} h_{d-c,0} \p{1+e^{-i\p{d-c}\c k}} \op{d}{c},
  &&
  \ut{\v{\m w}}_k \equiv \sum_{d\ne0} \tilde w_{dk} \ket{d},
  \label{eq:cycle_vecs}
\end{align}
in order to express \eqref{eq:cond_2_cycle} as the set of eigenvalue
equations
\begin{align}
  \ut{\check{\m h}}_k \c \ut{\v{\m w}}_k
  = \p{\Delta + 2 h_0} \ut{\v{\m w}}_k.
  \label{eq:cond_2_square}
\end{align}
The appearance of a wavenumber index $k$ in \eqref{eq:cond_2_square}
implies that all fixed-$k$ components of a general coefficient matrix
$\m w$ must simultaneously satisfy \eqref{eq:cond_2_square} in order
to generate states of fixed excitation energy $\Delta$ when the
corresponding perturbation $\V_2^\Delta$ acts on a fully symmetric
state $\ket\psi\in\M_0$.  The decomposition of an arbitrary
coefficient vector $\v{\m w}=\sum_\Delta\v{\m w}_\Delta$ into
coefficient vectors $\v{\m w}_\Delta$ that generate a fixed-energy
perturbation $\V_2^\Delta$ is then performed by projecting each
$k$-component of $\v{\m w}$ onto the corresponding $\Delta$-eigenspace
of $\ut{\check{\m h}}_k$.  If the perturbation $\V_2$ is
translationally invariant, then the $k$-components of $\v{\m w}$ for
all $k\ne 0$ all vanish, so we only need to consider the case of
$k=0$.

>>>>

We consider an array of $N$ multilevel spins with SU($n$)-symmetric
interactions that can be written in the form
\begin{align}
  H_0 = \sum_{p<q} h_{pq} \Pi_{pq},
  &&
  \Pi_{pq} \equiv \sum_{\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)},
  \label{eq:ints}
\end{align}
where $p,q$ index individual spins; $\mu,\nu$ index states in an
orthonormal basis for the $n$-dimensional Hilbert space $\H_n$ of a
single spin; $h_{pq}$ are scalar coefficients; the operator
$S_{\mu\nu}^{(p)}\equiv\op{\mu}{\nu}_p$ flips the state of spin $p$ to
$\ket\mu$ from $\ket\nu$; and the operator $\Pi_{pq}$ permutes the
states of spins $p$ and $q$.  The permutation operator $\Pi_{pq}$ is a
multilevel generalization of the SU(2)-symmetric spin interaction
$\v S_p\c\v S_q$ for $\v S=\p{s_\x,s_\y,s_\z}$, with $s_\alpha$ an
individual spin operator proportional to the Pauli matrix
$\sigma_\alpha$.

@@

Here we show that power-law SU($n$)-symmetric interactions of the form
in \eqref{eq:ints} with $h_{pq}=-h/\abs{p-q}^\alpha$ yield a
non-vanishing many-body interaction energy gap when $\alpha\le D$,
where $D$ is the dimension of the lattice.  On a periodic lattice of
$N=L^D$ spins, the spectral gap of the interaction Hamiltonian is (see
Appendix \ref{sec:trans_inv_single})
\begin{align}
  \Delta
  = \sum_{d\in\ZZ_L^D} h_{0,d} \sp{\cos\p{d \c k_{\t{SE}}}-1}
  = h \sum_{\substack{d\in\ZZ_L^D\\\abs{d}\ge1}}
  \f{1-\cos\p{d \c k_{\t{SE}}}}{\abs{d}^\alpha},
\end{align}
where the domain of $d$ is defined in terms of integers modulo $L$,
i.e.~$\ZZ_L\simeq\set{0,1,\cdots,L-1}$ with the relation $\simeq$
denoting an association that ignores the cyclic structure of $\ZZ_L$;
$k_{\t{SE}}\in\ZZ_L\times2\pi/L$ is a wavenumber for a singly-excited
spin-wave state; and the norm $\abs{d}$ for a vector $d$ on a periodic
lattice is implicitly understood to mean the smallest Euclidean
distance of $d$ from a fixed origin.  In order to yield the smallest
excitation energy $\Delta$, the wavenumber $k_{\t{SE}}$ should
maximize the contribution of the cosine term above, which is achieved
by a wavenumber that minimizes the oscillations of this term when
integrated over the entire lattice.  A suitable candidate for a
minimal wavenumber is $k_{\t{SE}}=\p{2\pi/L,0,0,\cdots}$, which
corresponds to an excitation energy
\begin{align}
  \Delta = h \sum_{\substack{d\in\ZZ_L^D\\\abs{d}\ge1}}
  \f{1-\cos\p{d_12\pi/L}}{\abs{d}^\alpha}.
\end{align}
Defining $\epsilon\equiv2/L$ and a rescaled domain symmetrized about
$0$, $\SS_\epsilon\simeq\ZZ_L/\epsilon$ with
$\SS_\epsilon\subset\sp{-1,1}$, we substitute $x\simeq\epsilon d$ to
get
\begin{align}
  \Delta
  = h \sum_{\substack{x\in\SS_\epsilon^D\\\abs{x}\ge\epsilon}}
  \f{1-\cos\p{\pi x_1}}{\abs{x/\epsilon}^\alpha}
  = h \epsilon^{\alpha-D} \sum_{\substack{x\in\SS_L^D\\\abs{x}\ge\epsilon}}
  \epsilon^D \f{1-\cos\p{\pi x_1}}{\abs{x}^\alpha}.
\end{align}
As $\epsilon\to0$ the discrete sum over $x$ becomes an integral that
avoids an infinitesimal region about the origin, i.e.
\begin{align}
  \Delta = h \epsilon^{\alpha-D} \I_{D\epsilon},
  &&
  \I_{D\epsilon}
  \equiv \int_{\TT_1^D\setminus\TT_\epsilon^D} \d^Dx\,
  \f{1-\cos\p{\pi x_1}}{\abs{x}^\alpha},
\end{align}
where the integral $\I_{D\epsilon}$ is defined using the interval
$\TT_a\equiv\p{-a,a}$.  The integrand of $\I_{D\epsilon}$ is strictly
positive and well-behaved on the entirety of its domain except for the
origin, where depending on the value of $\alpha$ the integrand may
vanish or diverge as $\abs{x}\to0$.  Together, these facts mean that
\begin{align}
  \I_{D\epsilon} \stackrel{\epsilon\to0}{\sim} \epsilon^{-\gamma},
  &&
  \Delta \stackrel{\epsilon\to0}{\sim} h \epsilon^{\alpha-D-\gamma},
\end{align}
for some $\gamma\ge0$, which implies that gap $\Delta$ is
non-vanishing when $\alpha\le D\le D+\gamma$.

@@

For reference, the single-body eigenvalue problem is
\begin{align}
  \p{\m h - \diag\v h}\c\v v = \Delta \v v,
  \label{eq:cond_1_ref}
\end{align}
where $\m h$ is a matrix of all couplings $h_{pq}$ that appear in the
interaction Hamiltonian $H_0$ in \eqref{eq:ints}; $\v h$ is a vector
of all $h_p\equiv\sum_q h_{pq}$; $\diag\v h$ is a matrix with $\v h$
on the diagonal and zeroes everywhere else; and $\v v$ is a vector of
coefficients used to construct the single-body perturbation
$\V_1\p{\v v}$ defined in \eqref{eq:perturbations}.  When the
interaction Hamiltonian $H_0$ is translationally invariant, the
couplings $h_{pq}$ depend only on the separation $\pm\p{p-q}$, so the
eigenvectors of $\m h$ are plane waves of the form
\begin{align}
  \v v_k \equiv \sum_p e^{ip\c k} \ket{p},
\end{align}
where on a $D$-dimensional periodic lattice of $N=L^D$ spins, lattice
sites are indexed by vectors
$p\in\ZZ_L^D\simeq\set{0,1,\cdots,L-1}^D$, and wavenumbers take on
values $k\in\ZZ_L^D\times2\pi/L$.  The corresponding eigenvalues of
$\m h$ can be determined by expanding
\begin{align}
  \m h\c\v v_k = \sum_{p,q} h_{pq} e^{iq\c k} \ket{p}
  = \sum_{p,d} h_{p,p+d} e^{i\p{p+d}\c k} \ket{p}
  = \sum_d h_{0,d} e^{id\c k} \v v_k
  = \sum_d h_{0,d} \cos\p{d\c k} \v v_k,
\end{align}
where the imaginary terms vanish because $h_{0,d}=h_{0,-d}$.  The
remainder of \eqref{eq:cond_1_ref} that we need to sort out is
$\diag\v h$, where all $h_p=\sum_qh_{pq}=\sum_dh_{0,d}$ are equal,
which implies that $\diag\v h=\sum_dh_{0,d}$ is a scalar.  We thus
find that
\begin{align}
  \p{\m h - \diag\v h}\c\v v_k = \Delta_k \v v_k,
  &&
  \Delta_k \equiv \sum_d h_{0,d} \sp{\cos\p{d\c k}-1}.
\end{align}

@@

The two-body eigenvalue equation in \eqref{eq:cond_2} is designed to
find solutions $\m w$ to the equation
\begin{align}
  \p{2h_{pq}-h_p-h_q} w_{pq}
  + \sum_k \p{h_{pk} w_{kq} + w_{pk} h_{kq}}
  = \Delta w_{pq},
  \label{eq:cond_2_ref_start}
\end{align}
where $h_p\equiv\sum_q h_{pq}$.  If the interaction Hamiltonian $H_0$
is translationally invariant, then the couplings $h_{pq}$ depend on
$p$ and $q$ only through the separation $\pm\p{p-q}$.  In this case,
all $h_p=h_0$ are equal, and \eqref{eq:cond_2_ref_start} can be
written in the form
\begin{align}
  2 \m h\circ \m w + \P_{\t{off-diag}}\p{\m h\c\m w + \m w\c\m h}
  = \p{\Delta + 2h_0} \m w,
  \label{eq:cond_2_ref}
\end{align}
where $\m h$ and $\m w$ are matrices of all $h_{pq}$ and $w_{pq}$, and
$\m h\circ\m w$ denotes an element-wise (Kronecker) product of $\m h$
and $\m w$, and
$\P_{\t{off-diag}}\p{\m m}\equiv \m m-\sum_p\op{p}\m m\op{p}$ denotes
the projection of $\m m$ onto the space of strictly off-diagonal
matrices.  In order to find solutions to \eqref{eq:cond_2_ref}, we we
expand the matrices $\m h,\m w$ in a basis that the respects
translational symmetry of $\m h$.  To this end, for all lattice
displacements $d\in\ZZ_L^D$ and wavenumbers $k\in\ZZ_L^D\times2\pi/L$
we define the {\it cycle matrices}
\begin{align}
  \m m_{dk} \equiv \sum_p e^{ip\c k} \op{p+d}{p},
  \label{eq:cycle}
\end{align}
where the element-wise sums in $p+d$ are implicitly taken modulo $L$
(i.e.~the length of the periodic lattice along each axis).  In terms of the cycle matrices, we define
\begin{align}
  \tilde w_{dk} \equiv \f1N \tr\p{\m m_{dk}^\dag \m w},
\end{align}
expand
\begin{align}
  \m h = \sum_{p,q} h_{pq} \op{p}{q}
  = \sum_{q,d} h_{q+d,q} \op{q+d}{q}
  = \sum_d h_{d,0} \m m_{d,0},
  &&
  \m w = \sum_{d,k} \tilde w_{dk} \m m_{dk},
\end{align}
and write the condition in \eqref{eq:cond_2_ref} as a new set of
conditions
\begin{align}
  \sum_{d\ne0} 2 h_{d,0} \tilde w_{dk} \m m_{dk}
  + \sum_{\substack{c,d\\c+d\ne0}}
  h_{c,0} \tilde w_{dk} \p{1 + e^{-ic\c k}} \m m_{c+d,k}
  = \p{\Delta + 2 h_0} \sum_{d\ne0} \tilde w_{dk} \m m_{dk},
\end{align}
that must hold for all wavenumbers $k$.  With some re-indexing, we can
write
\begin{align}
  \sum_{d\ne0} 2 h_{d,0} \tilde w_{dk} \m m_{dk}
  + \sum_{c,d\ne0} h_{d-c,0} \tilde w_{ck}
  \p{1 + e^{-i\p{d-c}\c k}} \m m_{dk}
  = \p{\Delta + 2 h_0} \sum_{d\ne0} \tilde w_{dk} \m m_{dk},
  \label{eq:cond_2_cycle}
\end{align}
and define
\begin{align}
  \ut{\check{\m h}}_k
  \equiv \sum_{d\ne0} 2 h_{d,0} \op{d}
  + \sum_{c,d\ne0} h_{d-c,0} \p{1+e^{-i\p{d-c}\c k}} \op{d}{c},
  &&
  \ut{\v{\m w}}_k \equiv \sum_{d\ne0} \tilde w_{dk} \ket{d},
  \label{eq:cycle_vecs}
\end{align}
in order to express \eqref{eq:cond_2_cycle} as the set of eigenvalue
equations
\begin{align}
  \ut{\check{\m h}}_k \c \ut{\v{\m w}}_k
  = \p{\Delta + 2 h_0} \ut{\v{\m w}}_k.
  \label{eq:cond_2_square}
\end{align}
The appearance of a wavenumber index $k$ in \eqref{eq:cond_2_square}
implies that all fixed-$k$ components of a general coefficient matrix
$\m w$ must simultaneously satisfy \eqref{eq:cond_2_square} in order
to generate states of fixed excitation energy $\Delta$ when the
corresponding perturbation $\V_2^\Delta$ acts on a fully symmetric
state $\ket\psi\in\M_0$.  The decomposition of an arbitrary
coefficient vector $\v{\m w}=\sum_\Delta\v{\m w}_\Delta$ into
coefficient vectors $\v{\m w}_\Delta$ that generate a fixed-energy
perturbation $\V_2^\Delta$ is then performed by projecting each
$k$-component of $\v{\m w}$ onto the corresponding $\Delta$-eigenspace
of $\ut{\check{\m h}}_k$.  If the perturbation $\V_2$ is
translationally invariant, then the $k$-components of $\v{\m w}$ for
all $k\ne 0$ all vanish, so we only need to consider the case of
$k=0$.
